|

### 2020-04-03 Paper 2020.Rmd
Includes submitted JOPskeleton

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark C. Hand"
date: "01/06/2018"
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}
- \doublespacing
---

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regression and first differences analyses to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find no relationship between the presence or level of campaign finance laws and quid pro quo corruption.[^SPSA]

[^SPSA]: Working paper presented at the Annual Meeting of the Southern Political Science Association, January 2019. Analysis available on [GitHub](https://github.com/markchand/Money-in-Politics).

```{r setup, include=FALSE}
# This is all necessary setup stuff, including packages and for Markdown
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
suppressMessages(library("tidyverse")) # everything 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library (MASS) # For binomial regression 
library(pglm) # For panel + binomial 
library(webshot) # For screenshots 
# library(psych) # Also for summary statistics
# library(texreg) # For regression outputs #fail 
# library(kableExtra) # For regression outputs 
# library(broom) # Because Matt Worthington said so 
# library(summarytools) # For summary statistics 
```

@@

```{r panel data wrangling, eval=T}
# Combining Barber and ICS 
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech. In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v. City of Berkeley-). Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v. Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v. Sorrell_, 2006).

<!--Those rulings have often been driven by the question of corporations’ participation in the political process. In 1978, the Court extended free speech protections to corporations (First National Bank of Boston v. Bellotti).

Then in 1990, it upheld a ban on corporations using treasury funds to pay for issue advertisements, arguing for an extended definition of corruption, "the corrosive and distorting effects of immense aggregations of wealth that are accumulated with the help of the corporate form and that have little or no correlation to the public's support for the corporation's political ideas" (Austin v. Michigan State Chamber of Commerce, later overturned).

In 1986, it  and struck down efforts to restrict their expenditures to FEC-registered Political Action Committees (FEC v. Massachusetts Right to Life). 
-->

@@

```{r Barber summary, eval=T}
# This is a summary, but includes all the 99999s and doesn't have skew in it. 
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

@@

```{r Barber summary statistics latex, results="asis", eval=TRUE}
# This is what fails to knit (see error below)
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F, 
          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
```

@@

## Methods

### Model I: Panel Regression
Having constructed a full 1990-2012 panel data set from these three data sets, I then run a set of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.

I include three predictor variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits. For each of these independent variables, I construct two variables for use in the model. The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are. The second is a continuous variable indicating the dollar amount of the limit in the state in that year. By interacting these two variables, I test two separate associations. The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits. The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year. After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year. These basic models are included in Appendix X.

I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption convictions, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels. For each of these models, I test fixed state and year effects and random effects. The models are as follows:

#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
$Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

#### Corruption Reflections Index versus campaign contributions in a given state-year: 
$Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

```{r modeling of initial correlations (with fixed effects), eval=T}
## CCI 
# Individual limits and corruption
CCIreg1  <- plm(CCI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No signifigance

# Individual-to-party limits and corruption
CCIreg2  <- plm(CCI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No Signifigance

# PAC Limits and corruption
CCIreg3  <- plm(CCI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No Signifigance

# Total Limits and corruption
CCIreg4  <- plm(CCI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# One star. Hmm...

# Everybody? 
CCIreg5 <- plm(CCI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")

## CRI
CRIreg1  <- plm(CRI ~ ind_limits_2010*ind_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No signifigance

# Individual-to-party limits and reflection
CRIreg2  <- plm(CRI ~ ind2pty_limits_2010*ind2pty_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# One star. Hmm...

# PAC Limits and reflection
CRIreg3  <- plm(CRI ~ pac_limits_2010*pac_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No Signifigance

# All Limits and reflection
CRIreg4  <- plm(CRI ~ total_limits_2010*total_limits_dummy,data = BarberICC, index = c("st","year"), effect="twoways")
# No Signifigance

# Everybody? 
CRIreg5 <- plm(CRI ~ ind_limits_2010*ind_limits_dummy + ind2pty_limits_2010*ind2pty_limits_dummy + pac_limits_2010*pac_limits_dummy, data = BarberICC, index = c("st","year"), effect="twoways")
```

```{r output of initial correlations (with fixed effects), include=F}
stargazer(CCIreg1, CCIreg2, CCIreg3, CCIreg5,CRIreg1, CRIreg2, CRIreg3, CRIreg5,
  type="text", 
  title = "Appendix A: Are campaign limits correlated with corruption convictions or reflections?",
  out="collateral/AppendixA.htm",
  dep.var.labels = c("Corruption Convictions Index","Corruption Reflections Index"),
  covariate.labels=c("Individual limit amounts", "Individual limits (dummy)","Individual-to-party limit amount","Individual-to-party limits (dummy)","PAC limit amounts","PAC limits (dummy)"),
  add.lines = list(c("Effects","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way","Two-Way"))
  )
```

```{r modeling of CCI base model effects, eval=T}
# Base model with no Two-Way or random effects 
cci.base.pooled <- plm(CCI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="pooling")

# Base model with fixed effects (NB: effect="individual" is redundant here)
cci.base.fixed <- plm(CCI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within")

# Base model with random effects 
cci.base.random <- plm(CCI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="random")

#Base model with fixed effects and time fixed effects 
cci.base.fixed.time <- plm(CCI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within", 
                   effect = "twoways")

# Base model with random effects doesn't work: 
# Error in solve.default(crossprod(ZBmu)) : 
  # system is computationally singular: reciprocal condition number = 1.96767e-18
```

```{r Hausman for CCI base model, eval=F}
phtest(cci.base.pooled, cci.base.fixed, cci.base.random, cci.base.fixed.time)

@@

```{r output of CCI base model effects}
stargazer(cci.base.pooled, 
          cci.base.fixed, 
          cci.base.random, 
          cci.base.fixed.time, 
          type="text",
          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
          )
```

```{r modeling of CRI base model effects, eval=T}
# Base model with no fixed or random effects 
 cri.base.pooled <- plm(CRI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="pooling")

# Base model with fixed effects (NB: effect="individual" is redundant here)
cri.base.fixed <- plm(CRI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within")

# Base model with random effects 
cri.base.random <- plm(CRI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="random")

#Base model with fixed effects and time fixed effects 
cri.base.fixed.time <- plm(CRI ~ jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within", 
                   effect = "twoways")
```

```{r Hausman for CRI base model, eval=F}
phtest(cri.base.pooled, cri.base.fixed, cri.base.random, cri.base.fixed.time)
```

```{r output of CRI base model effects}
stargazer(cri.base.pooled, 
          cri.base.fixed, 
          cri.base.random, 
          cri.base.fixed.time, 
          type="text",
          add.lines = list(c("Effects", "Pooled", "Fixed", "Random", "Two-Way"))
          )
```

```{r modeling of CCI with campaign finance variables, eval=T}
# Base model with no fixed or random effects 
 cci.limits.pooled <- plm(CCI 
                   ~ ind_limits_2010*ind_limits_dummy 
                   + ind2pty_limits_2010*ind2pty_limits_dummy 
                   + pac_limits_2010*pac_limits_dummy
                   + jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="pooling")

# Base model with fixed effects (NB: effect="individual" is redundant here)
cci.limits.fixed <- plm(CCI 
                   ~ ind_limits_2010*ind_limits_dummy 
                   + ind2pty_limits_2010*ind2pty_limits_dummy 
                   + pac_limits_2010*pac_limits_dummy
                   + jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within")

# Base model with random effects (failed)  
# cci.limits.random <- plm(CCI 
#                    ~ ind_limits_2010*ind_limits_dummy 
#                    + ind2pty_limits_2010*ind2pty_limits_dummy 
#                    + pac_limits_2010*pac_limits_dummy
#                    + jdiv  # Divided government 
#                    + bindingonetermlimit # Binding one-term limit 
#                    + bindingtwotermlimit # Binding two-term limit 
#                    + rpcinc_annual_new # Real per capita income ($1000)
#                    + eopop # AUSAs per million population
#                    + unemp # Unemployment 
#                    + citi6006 # Citizen ideology measure 
#                    + high_school + # Percent high school graduates
#                    + rgenrevpc # Real per capita gov revenues ($1000)
#                    + men_ineqincwag # Inequality: Male wages
#                    + grelimp # Relative government wages
#                    + urbanization_2 # Urbanization 
#                    + logpop, # Log of population (millions)
#                    data = AltBarber, 
#                    model="random")

#Base model with fixed effects and time fixed effects 
cci.limits.fixed.time <- plm(CCI 
                   ~ ind_limits_2010*ind_limits_dummy 
                   + ind2pty_limits_2010*ind2pty_limits_dummy 
                   + pac_limits_2010*pac_limits_dummy
                   + jdiv  # Divided government 
                   + bindingonetermlimit # Binding one-term limit 
                   + bindingtwotermlimit # Binding two-term limit 
                   + rpcinc_annual_new # Real per capita income ($1000)
                   + eopop # AUSAs per million population
                   + unemp # Unemployment 
                   + citi6006 # Citizen ideology measure 
                   + high_school + # Percent high school graduates
                   + rgenrevpc # Real per capita gov revenues ($1000)
                   + men_ineqincwag # Inequality: Male wages
                   + grelimp # Relative government wages
                   + urbanization_2 # Urbanization 
                   + logpop, # Log of population (millions)
                   data = AltBarber, 
                   model="within", 
                   effect = "twoways")

@@

### Modeling changes in campaign limits and corruption convictions

The final set of models (Table X) displays results from multiple first difference models designed to isolate the effect of changes in campaign finance laws on corruption convictions. None of the models find correlation between campaign finance limits and corruption convictions or corruption reflections.

>>>>

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark C. Hand"
date: ""
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}
- \doublespacing
---

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limts on donations to parties. Applying these methods to recently developed measures of media mentions of corruption suggests that these data may require further development.[^SPSA]

[^SPSA]: An earlier version of this paper was presented at the Annual Meeting of the Southern Political Science Association in January 2019. Analyses available on [GitHub](https://github.com/markchand/Money-in-Politics).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library (MASS) # For binomial regression 
library(tidyverse) # everything; placed here because of MASS::select() overlap 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library(pglm) # For panel + binomial 
library(webshot) # For screenshots 
library(viridis) # For colorblindedness
library(GGally) # For ggpairs
library(lm.beta) # For standardized regression coefficients 
library(broom) # for augment()
theme_set(theme_classic()) # Sets default theme

@@

```{r panel data wrangling,eval=T}
# Combining Barber and ICS  
corruption <- full_join(convictions, reflections)
corruption <- corruption %>% 
  rename("st"="State", "year"="Year")
corruption$st <- state.abb[match(corruption$st,state.name)]
BarberICC <- left_join(Barber, corruption)

@@

Apart from McCain-Feingold, for forty years all changes in the landscape of campaign finance have come from the Supreme Court and appellate courts, which have worked to balance questions of corruption with those of free speech. In 1981, the Court struck down contribution limits related to ballot measures (_Citizens against Rent Control v. City of Berkeley_). Just before the passage of McCain-Feingold, the courts considered state-level limits, allowing low limits in Missouri (_Nixon v. Shrink Missouri_, 2000), though it would later finding Vermont's to be low enough that they had a meaningful impact on political speech (_Randall v. Sorrell_, 2006).

@@

```{r Barber summary, eval=T,include=F}
# This is a summary, but includes all the 99999s and doesn't have skew in it.  
# stargazer(as.data.frame(subset(Barber[,3:6])), type="text", digits=0)

@@

```{r Barber summary stats latex, results="asis",eval=T,include=F}
# This is what fails to knit (see error below) 
stargazer(as.data.frame(subset(BarberNAs[,3:6])), digits=0, type="latex", title="Descriptive Statistics for State Level Campaign Finance Limits", covariate.labels = c("Individual Limits","Individual-to-Party Limits","Party Limits", "PAC Limits"), header=F, 
          notes = "Notes: 'N' equals number of state-years (out of n=1150) in which that type of limit is present") 
```

@@

## Methods
Having constructed a full 1990-2012 panel data set from these three data sets, I then run a series of time series regressions testing the relationship between contribution limits and both dependent variables, the Corruption Convictions Index and the Corruption Reflections Index.

I include three study variables in both sets of models: Individual contribution limits, individual-to-party contribution limits, and PAC contribution limits. For each of these independent variables, I construct two variables for use in the models. The first is a dummy variable indicating whether there are contribution limits in that state in that year, coded as “0” if there are no limits and “1” if there are. The second is a continuous variable indicating the dollar amount of the limit in the state in that year. By interacting these two variables, I test two separate associations. The dummy variable tests whether there is a difference in the CCI and CRI in states with limits versus states without limits. The continuous variable tests whether higher or lower limits are associated with higher or lower CCI and CRI scores, within the group of states that have limits in a given year. After performing this transformation on all three independent variables, I test two initial sets of models: (1) Corruption Convictions Index versus campaign contribution limits in a given state-year, and (2) Corruption Reflections Index versus campaign contributions in a given state-year. <!--These basic models are included in Appendix X.-->

I build a model of political corruption using control variables previously demonstrated by Alt and Lassen to be correlated with corruption convictions, resulting in a data set covering 1990-2004, the period of overlap among the data sets listed above. These include controlling for the size and education levels of the population, the ideology of a population, income levels and inequality, education levels, the number and relative income of government employees, and urbanization. Building a model of corruption that includes variables previously demonstrated to be correlated with corruption levels, then adding in campaign finance data, I can better identify the association of campaign finance laws with corruption levels. For each of these models, I test fixed state and year effects and random effects. I also test appropriate transformations of both dependent and independent variables. The models are as follows:

#### Corruption Convictions Index versus campaign contribution limits in a given state-year: 
$(log)Convictions = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

#### Corruption Reflections Index versus campaign contributions in a given state-year: 
$(log)Reflections = \alpha_{state} + \beta_{1}{indiv.dummy} + \beta_{2}{indiv.dummy}*{indiv.limit} + \beta_{3}{pac.dummy} + \beta_{4}{pac.dummy}*{pac.limit} + \beta_{5}{indiv-to-party.dummy} + \beta_{6}{indiv-to-party.dummy}*{indiv-to-party.limit} + Controls + \epsilon$

```{r data visualization, eval=T,include=F}
# Per Bill's request to see about logging data:  
AltBarber %>% 
  #select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy,jdiv,bindingonetermlimit,bindingtwotermlimit,rpcinc_annual_new,eopop,unemp,citi6006,high_school,rgenrevpc,men_ineqincwag,grelimp,urbanization_2,logpop) %>% 
  dplyr::select(CCI,CRI,ind_limits_2010,ind_limits_dummy,ind2pty_limits_2010,ind2pty_limits_dummy,pac_limits_2010,pac_limits_dummy) %>%
  ggpairs(cardinality_threshold = 21)

AltBarber %>% 
  ggplot() +
  geom_histogram(aes(log(CRI))) # LOG

AltBarber %>% 
  ggplot() +
  geom_histogram(aes(log(CCI))) # LOG

AltBarber %>% 
  filter(ind_limits_2010!=99999) %>% 
  ggplot() +
  geom_histogram(aes(log(ind_limits_2010))) # Log. Remember that 99999s == no limit. Have to leave as 99999 for the same reason that Barber did; otherwise NAs get dropped.

AltBarber %>% 
  filter(pac_limits_2010!=99999) %>% 
  ggplot() +
  geom_histogram(aes(log(pac_limits_2010))) # Log

AltBarber %>% 
  filter(ind2pty_limits_2010!=99999) %>% 
  ggplot() +
  geom_histogram(aes(log(ind2pty_limits_2010))) # Log 
```

```{r CCI models, eval=T, include=F}
cci <- plm(CCI ~ jdiv  # Divided government  
           + bindingonetermlimit # Binding one-term limit 
           + bindingtwotermlimit # Binding two-term limit 
           + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="pooling")

cci.log <- plm(log(CCI+1) ~ jdiv  # Divided government 
           + bindingonetermlimit # Binding one-term limit 
           + bindingtwotermlimit # Binding two-term limit 
           + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="pooling")

cci.log.pars <- plm(log(CCI+1) ~ 
             jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="pooling")

cci.log.iv <- plm(log(CCI+1) ~ 
           ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="pooling")

cci.log.iv.log <- plm(
           log(CCI+1) ~ log(ind_limits_2010)*ind_limits_dummy 
           + log(ind2pty_limits_2010)*ind2pty_limits_dummy 
           + log(pac_limits_2010)*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="pooling")

cci.log.iv.fixed <- plm(
           log(CCI+1) ~ 
           ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within")

cci.log.iv.fixed.time <- plm(log(CCI+1) ~ 
           ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber, 
           model="within",
           effect="twoways")

@@

```{r CCI models output, eval=T,results="asis"}
stargazer(
  cci.log.pars, 
  cci.log.iv, # F Stat down? 
  cci.log.iv.log, # F Stat down further 
  #cci.log.iv.fixed, # AR2 Stat bottoms out 
  cci.log.iv.fixed.time, 
  type="latex",
  #out = "collateral/test.htm",
  font.size = "small",
  header=FALSE, 
  column.sep.width = "-15pt", 
  digits = 2, digits.extra = 0, 
  no.space = TRUE,
  title = "Models of Contribution Limits and Corruption Convictions",
  dep.var.labels = "Corruption Convictions Index (logged)",
  covariate.labels=c("Individual limit (amount)",
                     "Individual limit (logged)",
                     "Individual limit (dummy)",
                     "Individual-to-party limit (amount)",
                     "Individual-to-party limit (logged)",
                     "Individual-to-party limit (dummy)",
                     "PAC limit (amount)",
                     "PAC limit (logged)",
                     "PAC limit (dummy)",
                     "Divided government",
                     "AUSAs per population (MMs)"),
                     # "% high school grads",
                     # "Govt revenues/capita ($1000s)",
                     # "Urbanization",
                     # "Log of population (MMs)"),
  add.lines = list(c(" ","Base Model","With IVs","Pooled","FE"))
  )

# If I'm interpreting stuff correctly, then: The model that performed best was a logged CCI, non-logged IVs, with no fixed time or state effects. In that model, one campaign finance limits (ind2pty_limits_dummy) was associated with higher corruption; one (pac_limits_2010) was associated with lower corruption. This is even theoretically stranger than the preivous model.

@@
